Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-05-25 manuscript-figures.Rmd
figure edits

## Compute mosquito thermal tolerance range (minimum and maximum)
MosqThermRange_df <- mean.Vec %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
  )) %>%
  group_by(system_label) %>%
  filter(V0 > 0) %>%
  mutate(CTmin_V0 = min(Temperature)) %>%
  mutate(CTmax_V0 = max(Temperature)) %>%
  select(system_ID, system_label, CTmin_V0, CTmax_V0) %>%
  distinct()

# Title names for each mosquito+pathogen combination (NB: to be added to get-analysis-dfs.R)
data.R0 <- data.R0 %>%
  ungroup() %>% 
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
  ))

# ## Add a "point at infinity" for sigmaH
# # Value of sigmaH to replace 'Inf' with for plotting
# infinite_skew <- 10^3 + 2500
# 
# # Get the largest value of log10(sigmaH)
# max_log10sigmaH <- filter(AllOutputs, is.finite(sigmaH)) %>%
#   select(sigmaH) %>%
#   max() %>%
#   log10()
# 
# # Used to create a gap dividing finite and infinite sigmaH
# infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
# 
# # add a second proxy sigmaH point at infinity to make the values easier to see there
# temp <- filter(AllOutputs, is.infinite(sigmaH)) %>%
#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
# AllOutputs <- mutate(AllOutputs, sigmaH_proxy = ifelse(is.finite(sigmaH),
#                                                        sigmaH, infinite_skew
# ))
# AllOutputs <- add_row(AllOutputs, temp) %>% distinct()
# 
# # Define sigmaH tick breaks and labels
# sigmaH_breaks <- c(10^c(seq(0, 3, by = 1)), infinite_divide, infinite_skew)
# sigmaH_labels <- c(paste(c(10^c(seq(0, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
# 
# ## Parasite thermal characteristics
# ThermPathChars <- read_csv("results/ThermalCharacteristics.csv", show_col_types = FALSE)
# 
# # Title names for each mosquito+pathogen combination
# ThermPathChars <- ThermPathChars %>%
#   mutate(system_label = case_when(
#     system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* & DENV",
#     system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
#     system_ID == "Aedes albopictus+DENV" ~ "(c) *Ae. albopictus* & DENV",
#     system_ID == "Anopheles spp.+P.fal." ~ "(d) *Anopheles* spp. & *P. falciparum*",
#     system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
#   ))
# ## Add a "point at infinity" for sigmaH (NB: to be added to get-analysis-dfs.R)
# # Value of sigmaH to replace 'Inf' with for plotting
# infinite_skew <- 10^3 + 2500
# 
# # Get the largest value of log10(sigmaH)
# max_log10sigmaH <- filter(ThermPathChars, is.finite(sigmaH)) %>%
#   select(sigmaH) %>%
#   max() %>%
#   log10()
# 
# # Used to create a gap dividing finite and infinite sigmaH
# infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
# 
# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
# ThermPathChars <- mutate(ThermPathChars, sigmaH_proxy = ifelse(is.finite(sigmaH),
#                                                                sigmaH, infinite_skew
# ))
# # add a second proxy sigmaH point at infinity to make the values easier to see there
# temp <- filter(ThermPathChars, is.infinite(sigmaH)) %>%
#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
# 
# ThermPathChars <- add_row(ThermPathChars, temp) %>%
#   arrange(sigmaH_proxy) %>%
#   distinct()
# 
# ## Options
# # Define sigmaH tick breaks and labels
# sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
# sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

@@

data.R0_norm <- data.R0 %>% 
  ungroup() %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* & *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
  )) %>%
  filter(KH %in% newKH_vals) %>% 
  filter(variable == "R0") %>%
  select(-variable) %>%
  # normalize variables to have a maximum of 1
  group_by(system_ID, Model, sigmaH, KH) %>% 
  # mutate(mean_norm = mean / max(mean)) %>% 
  mutate(median_norm = median / max(median)) %>%
  # mutate(highHCI_norm = highHCI / max(median)) %>% 
  # mutate(lowHCI_norm = lowHCI / max(median)) %>% 
  arrange(system_ID, sigmaH, KH, Temperature, median_norm)

@@

Toptalt_df <- data.Topt %>%
  ungroup() %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* & DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* & ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c) *Ae. albopictus* & DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *Anopheles* spp. & *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* & WNV"
  )) %>% 
  distinct() %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, KH, mean) %>% 
  mutate(sigmaH_proxy = sigmaH)

@@

# Plot mean of Topt heat map
Toptalt_plots <- Toptalt_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = transmission thermal optimum
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
  # Topt for FINITE sigmaH:
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy < 10^2.2),
    breaks = Topt_breaks
  ) +
  # Topt for INFINITE sigmaH:
  # take mean of mean to hide variation from artifacts of uncertainty 
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy > infinite_skew) %>% 
      group_by(system_ID) %>% 
      mutate(mean = mean(mean), .groups = "keep"),
    size = 1,
    breaks = Topt_breaks
  ) +
  # # R0 = 1 contour: cheat and use where CTwidth = 0 (i.e. where R0<1 at any temperature)
  geom_contour(data = filter(data.CT, variable == "CTwidth"),
               aes(y = sigmaH, z = mean, colour = "R0 = 1"), 
               breaks = min(filter(data.CT, variable == "CTwidth", mean > 0)$mean),
               size = 1) +
  # geom_contour(data = data.R0_norm,
  #              aes(y = sigmaH, z = mean, colour = "R0=1"), breaks = c(1), size = 1) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +

@@

CTwidth_df <- data.CT %>%
  filter(variable == "CTwidth") %>% 
  mutate(sigmaH_proxy = sigmaH) %>% 
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, median) %>% 
  ungroup()

@@

CTWidth_heat_plots <- CTwidth_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal mean_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = mean)) +
  # CTwidth for FINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < infinite_divide**0.99)) +
  # CTwidth for INFINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy > infinite_divide**1.01)) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # color:
  scale_fill_viridis_d(
    name = "Parasite thermal tolerance\nrange width (°C)",
    option = "plasma"
  ) +
  # faceting:
  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top", title.hjust = 0.5,
    barwidth = unit(5, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(16) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

>>>>

## Compute mosquito thermal tolerance range (minimum and maximum)
MosqThermRange_df <- mean.Vec %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
  )) %>%
  group_by(system_label) %>%
  filter(V0 > 0) %>%
  mutate(CTmin_V0 = min(Temperature)) %>%
  mutate(CTmax_V0 = max(Temperature)) %>%
  select(system_ID, system_label, CTmin_V0, CTmax_V0) %>%
  distinct()

# Title names for each mosquito+pathogen combination (NB: to be added to get-analysis-dfs.R)
data.R0 <- data.R0 %>%
  ungroup() %>% 
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
  ))

# ## Add a "point at infinity" for sigmaH
# # Value of sigmaH to replace 'Inf' with for plotting
# infinite_skew <- 10^3 + 2500
# 
# # Get the largest value of log10(sigmaH)
# max_log10sigmaH <- filter(AllOutputs, is.finite(sigmaH)) %>%
#   select(sigmaH) %>%
#   max() %>%
#   log10()
# 
# # Used to create a gap dividing finite and infinite sigmaH
# infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
# 
# # add a second proxy sigmaH point at infinity to make the values easier to see there
# temp <- filter(AllOutputs, is.infinite(sigmaH)) %>%
#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
# AllOutputs <- mutate(AllOutputs, sigmaH_proxy = ifelse(is.finite(sigmaH),
#                                                        sigmaH, infinite_skew
# ))
# AllOutputs <- add_row(AllOutputs, temp) %>% distinct()
# 
# # Define sigmaH tick breaks and labels
# sigmaH_breaks <- c(10^c(seq(0, 3, by = 1)), infinite_divide, infinite_skew)
# sigmaH_labels <- c(paste(c(10^c(seq(0, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
# 
# ## Parasite thermal characteristics
# ThermPathChars <- read_csv("results/ThermalCharacteristics.csv", show_col_types = FALSE)
# 
# # Title names for each mosquito+pathogen combination
# ThermPathChars <- ThermPathChars %>%
#   mutate(system_label = case_when(
#     system_ID == "Aedes aegypti+DENV" ~ "(a) *Ae. aegypti* and DENV",
#     system_ID == "Aedes aegypti+ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
#     system_ID == "Aedes albopictus+DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
#     system_ID == "Anopheles spp.+P.fal." ~ "(d) *An. gambiae* and *P. falciparum*",
#     system_ID == "Culex quinquefasciatus+WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
#   ))
# ## Add a "point at infinity" for sigmaH (NB: to be added to get-analysis-dfs.R)
# # Value of sigmaH to replace 'Inf' with for plotting
# infinite_skew <- 10^3 + 2500
# 
# # Get the largest value of log10(sigmaH)
# max_log10sigmaH <- filter(ThermPathChars, is.finite(sigmaH)) %>%
#   select(sigmaH) %>%
#   max() %>%
#   log10()
# 
# # Used to create a gap dividing finite and infinite sigmaH
# infinite_divide <- 10^mean(c(3, log10(infinite_skew)))
# 
# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
# ThermPathChars <- mutate(ThermPathChars, sigmaH_proxy = ifelse(is.finite(sigmaH),
#                                                                sigmaH, infinite_skew
# ))
# # add a second proxy sigmaH point at infinity to make the values easier to see there
# temp <- filter(ThermPathChars, is.infinite(sigmaH)) %>%
#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
# 
# ThermPathChars <- add_row(ThermPathChars, temp) %>%
#   arrange(sigmaH_proxy) %>%
#   distinct()
# 
# ## Options
# # Define sigmaH tick breaks and labels
# sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
# sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

@@

data.R0_norm <- data.R0 %>% 
  ungroup() %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
  )) %>%
  filter(KH %in% newKH_vals) %>% 
  filter(variable == "R0") %>%
  select(-variable) %>%
  # normalize variables to have a maximum of 1
  group_by(system_ID, Model, sigmaH, KH) %>% 
  # mutate(mean_norm = mean / max(mean)) %>% 
  mutate(median_norm = median / max(median)) %>%
  # mutate(highHCI_norm = highHCI / max(median)) %>% 
  # mutate(lowHCI_norm = lowHCI / max(median)) %>% 
  arrange(system_ID, sigmaH, KH, Temperature, median_norm)

@@

Toptalt_df <- data.Topt %>%
  ungroup() %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
  )) %>% 
  distinct() %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, KH, mean) %>% 
  mutate(sigmaH_proxy = sigmaH)

@@

# Plot mean of Topt heat map
Toptalt_plots <- Toptalt_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = transmission thermal optimum
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
  # Topt for FINITE sigmaH:
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy < 10^2.2),
    breaks = Topt_breaks
  ) +
  # Topt for INFINITE sigmaH:
  # take mean of mean to hide variation from artifacts of uncertainty 
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy > infinite_skew) %>% 
      group_by(system_ID) %>% 
      mutate(mean = mean(mean), .groups = "keep"),
    size = 1,
    breaks = Topt_breaks
  ) +
  # # R0 = 1 contour: cheat and use where CTwidth = 0 (i.e. where R0<1 at any temperature)
  geom_contour(data = filter(data.CT, variable == "CTwidth", sigmaH < infinite_divide),
               aes(y = sigmaH, z = mean, colour = "R0 = 1"), 
               breaks = min(filter(data.CT, variable == "CTwidth", mean > 0)$mean),
               size = 1) +
  # geom_contour(data = data.R0_norm,
  #              aes(y = sigmaH, z = mean, colour = "R0=1"), breaks = c(1), size = 1) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +

@@

CTwidth_df <- data.CT %>%  
  ungroup() %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
  )) %>% 
  filter(variable == "CTwidth") %>% 
  # filter(sigmaH < 10^2.2) %>% 
  mutate(sigmaH_proxy = sigmaH) %>% 
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, median) %>% 
  ungroup()

@@

CTWidth_heat_plots <- CTwidth_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal mean_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = mean)) +
  # CTwidth for FINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < 10^2.2)) +
  # CTwidth for INFINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, 
                                    sigmaH_proxy > 10^2.4, 
                                    sigmaH_proxy < infinite_divide)) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # color:
  scale_fill_viridis_d(
    name = "Parasite thermal tolerance\nrange width (°C)",
    option = "plasma"
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top", title.hjust = 0.5,
    barwidth = unit(5, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(16) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
